---
title: "SEINRD Model Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SEINRD Model Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(rSimpleModel)
library(rDataPipeline)
library(here)
library(magick)
library(pdftools)

i_am(path = "vignettes/SEINRD.Rmd")
knitr::opts_knit$set(root.dir = here())
```

## *config.yaml* file

The user should write a *config.yaml* file containing information pertaining to
the data products used in the code run. The example *config.yaml* file below 
describes a code run with inputs:

* `disease/sars_cov2/SEINRD_model/parameters/static_params`
* `disease/sars_cov2/SEINRD_model/parameters/rts`
* `disease/sars_cov2/SEINRD_model/parameters/efoi`

These inputs are listed in the `register` block, meaning that they should be 
downloaded to the local data store from an external source, with associated
metadata stored in the local registry. These inputs are automatically converted 
into a `read` block by `fair run` (when data products are already present in 
the data registry, inputs should be listed in the `read` block).

A code run usually also has outputs, which are listed in the `write` block. In
the example below, our outputs are:

* disease/sars_cov2/SEINRD_model/results/model_output
* disease/sars_cov2/SEINRD_model/results/figure

*SEINRDconfig.yaml*:
```{r config, echo=FALSE, comment=''}
cat(readLines(file.path(here(), 'inst/extdata/SEINRDconfig.yaml')), sep = '\n')
```

The submission script should call `initialise()` to set up the code run, 
then perhaps read in some data using one of the `read_*()` functions (for 
internal file formats) or `link_read()` (for external file formats such as 
csvs). The data might now be processed in some way, or a model / analysis might
bw carried out, after which the results should be saved in the local data store
via one of the `write_*()` functions or `link_write()`. When the code run is 
complete, `finalise()` should be called to register the all metadata with the
local registry.

## `fair pull`

Using the CLI tool, `fair pull` identifies any data products listed in the 
`register` field of the *config.yaml*. These data products are downloaded to
the local data store whilst associated metadata is registered in the local 
registry.

```{bash}
fair init --ci
fair pull inst/extdata/SEINRDconfig.yaml
```

The local registry should now contain three data products: 

1. `disease/sars_cov2/SEINRD_model/parameters/static_params`,
2. `disease/sars_cov2/SEINRD_model/parameters/rts`, and 
3. `disease/sars_cov2/SEINRD_model/parameters/efoi`.

## `fair run`

Again using the CLI tool, `fair run` performs the code run, as written in the.
submission script. In preparation for this, it translates the user-written 
*config.yaml* file for use by the Data Pipeline API. Any variables / wildcards 
specified by the user in the config file are cross referenced with the registry, 
and any data products registered by `fair pull` are made available to read by 
the current code run. 

```{bash}
fair run inst/extdata/SEINRDconfig.yaml
```

## Outputs

```{r, echo=FALSE}
path <- get_dataproduct(data_product = "disease/sars_cov2/SEINRD_model/results/figure",
                        version = "0.0.1",
                        namespace = "testing")
image_read_pdf(path, density = 60)
```

## Provenance report

```{r, echo=FALSE}
get_provenance(data_product = "disease/sars_cov2/SEINRD_model/results/model_output",
               version = "0.0.1",
               namespace = "testing")
```
