---
title: "SEIRS Model Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SEIRS Model Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)


```

```{r setup, include = FALSE}
library(rSimpleModel)
library(rDataPipeline)
library(dplyr)
library(RCurl)
library(deSolve)
library(ggplot2)
library(here)

here::i_am(path = "vignettes/SEIRS.Rmd")

dat <- c(alpha = 0, beta = 0.21, inv_gamma = 14,  inv_omega = 1, 
         inv_mu = 76, inv_sigma = 7, R0 = 3)
dat <- data.frame(param = names(dat), value = dat)
row.names(dat) <- NULL
# write.csv(dat, file.path(here(), "inst", "extdata", "static_params_SEIRS.csv"))
static_params <- dat
# Static parameters of the model
# static_params <- getURL("https://raw.githubusercontent.com/FAIRDataPipeline/rSimpleModel/main/inst/extdata/static_params_SEIRS.csv") %>% read.csv(text = .)
```

## *config.yaml* file

The user should write a *config.yaml* file containing information pertaining to
the data products used in the code run. The example *config.yaml* file below 
describes a code run with inputs:

* `disease/sars_cov2/SEIRS_model/parameters/static_params`

These inputs are listed in the `register` block, meaning that they should be 
downloaded to the local data store from an external source, with associated
metadata stored in the local registry. These inputs are automatically converted 
into a `read` block by `fair run` (when data products are already present in 
the data registry, inputs should be listed in the `read` block).

A code run usually also has outputs, which are listed in the `write` block. In
the example below, our outputs are:

* disease/sars_cov2/SEIRS_model/results/model_output
* disease/sars_cov2/SEIRS_model/results/figure

*config.yaml*:
```{r config, echo=FALSE, comment=''}
cat(readLines(file.path(here(), 'inst/extdata/SEIRSconfig.yaml')), sep = '\n')
```

## `fair pull`

Using the CLI tool, `fair pull` identifies any data products listed in the 
`register` field of the *config.yaml*. These data products are downloaded to
the local data store whilst associated metadata is registered in the local 
registry.

```{python, eval=FALSE}
fair pull config.yaml
```

```{r, include = FALSE}
# Run 
# setwd("/Users/Soniam/Desktop/git/FAIRDataPipeline/FAIR-CLI")
# tmp <- tempfile(fileext = ".sh")
# cat(paste("#!/bin/sh\n", 
#           "cd /Users/Soniam/Desktop/git/FAIRDataPipeline/SimpleModel/\n", 
#           "fair pull inst/extdata/config1.yaml\n",
#           "fair run --ci --debug inst/extdata/config1.yaml\n"), file = tmp)
# system2("chmod", paste("+x", tmp))
# 
# system2("/Users/Soniam/.poetry/bin/poetry", paste("run", tmp), 
#         stdout = TRUE)
```

```{r, include = FALSE}
config_file <- file.path(here(), "config.yaml")
data_static <- "disease/sars_cov2/SEIRS_model/parameters/static_params"

init <- configr::read.config(file = file.path(here::here(), "ci.yaml"))

create_config(path = config_file,
              description = "SEIRS Model",
              input_namespace = init$namespaces$input,
              output_namespace = init$namespaces$output,
              write_data_store = init$registries$local$data_store,
              local_repo = init$git$local_repo,
              force = TRUE)
add_write(path = config_file,
          data_product = data_static,
          description = "Static parameters of the model",
          file_type = "csv")

fair_run(path = config_file, skip = TRUE)

# Initialise code run
config <- file.path(Sys.getenv("FDP_CONFIG_DIR"), "config.yaml")
script <- file.path(Sys.getenv("FDP_CONFIG_DIR"), "script.sh")
handle <- initialise(config, script)

path <- link_write(handle, data_static)
write.csv(static_params, path)

finalise(handle)
```

The local registry should now contain three data products: 

1. `disease/sars_cov2/SEIRS_model/parameters/static_params`,
2. `disease/sars_cov2/SEIRS_model/parameters/rts`, and 
3. `disease/sars_cov2/SEIRS_model/parameters/efoi`.

## `fair run`

Again using the CLI tool, `fair run` performs the code run, as written in the.
submission script. In preparation for this, it translates the user-written 
*config.yaml* file for use by the Data Pipeline API. Any variables / wildcards 
specified by the user in the config file are cross referenced with the registry, 
and any data products registered by `fair pull` are made available to read by 
the current code run. 

```{r, include=FALSE}
config_file <- file.path(here(), "config2.yaml")
data_static <- "disease/sars_cov2/SEIRS_model/parameters/static_params"
results_dp <- "disease/sars_cov2/SEIRS_model/results/model_output"
figure_dp <- "disease/sars_cov2/SEIRS_model/results/figure"
init <- configr::read.config(file = file.path(here::here(), "ci.yaml"))

create_config(path = config_file,
              description = "SEIRS Model",
              input_namespace = init$namespaces$input,
              output_namespace = init$namespaces$output,
              write_data_store = init$registries$local$data_store,
              local_repo = init$git$local_repo,
              force = TRUE)
add_read(path = config_file,
         data_product = data_static)
add_write(path = config_file,
          data_product = results_dp,
          description = "SEIRS model results",
          file_type = "csv")
add_write(path = config_file,
          data_product = figure_dp,
          description = "SEIRS output plot",
          file_type = "pdf")

fair_run(path = config_file, skip = TRUE)
```

```{python, eval=FALSE}
fair run config.yaml
```

## *submission script*

The submission script should call `initialise()` to set up the code run, 
then perhaps read in some data using one of the `read_*()` functions (for 
internal file formats) or `link_read()` (for external file formats such as 
csvs). The data might now be processed in some way, or a model / analysis might
bw carried out, after which the results should be saved in the local data store
via one of the `write_*()` functions or `link_write()`. When the code run is 
complete, `finalise()` should be called to register the all metadata with the
local registry.

*vignettes/SEIRS.R*:
```{r, message=FALSE}
# Initialise code run
config <- file.path(Sys.getenv("FDP_CONFIG_DIR"), "config.yaml")
script <- file.path(Sys.getenv("FDP_CONFIG_DIR"), "script.sh")
handle <- initialise(config, script)

# Read code run inputs
static_params <- link_read(handle, "disease/sars_cov2/SEIRS_model/parameters/static_params") %>% 
  read.csv(row.names = 1)

# Run the model
results <- SEIRS_model(S = 0.999, 
                       E = 0.001,
                       I = 0, 
                       R = 0, 
                       timesteps = 1000,
                       alpha = filter(static_params, param == "alpha")$value, 
                       beta = filter(static_params, param == "beta")$value, 
                       inv_gamma = filter(static_params, param == "inv_gamma")$value,
                       inv_omega = filter(static_params, param == "inv_omega")$value, 
                       inv_mu = filter(static_params, param == "inv_mu")$value,
                       inv_sigma = filter(static_params, param == "inv_sigma")$value)

g <- plot_SEIRS(results)

# Save outputs to data store
path <- link_write(handle, "disease/sars_cov2/SEIRS_model/results/model_output") 
write.csv(results, path)

path <- link_write(handle, "disease/sars_cov2/SEIRS_model/results/figure") 
ggsave(path, g)

# Register code run in local registry
finalise(handle)
```

```{r, echo=FALSE, fig.height=4, fig.width=6}
g
```
